% !TEX root = ../main.tex

\begin{digest}
  Digitalization is the advanced stage of the development of information technology and the main driving force of digital economy. With the rapid development of the new generation of digital technology, all walks of life create more and more value by using digital technology, which promotes all walks of life to accelerate the digital transformation.



The digitalization mentioned in this paper mainly refers to the digital transformation of specific business and scene by using digital technology. The digital technology revolution has promoted the digital transformation of mankind. The economy of human society with the progress of technology evolved, farming technology opens the agricultural economy, industrial revolution to realize the evolution of the agricultural economy to industrial economy, now the digital technology revolution, to promote the digital revolution of human production and living, gives birth to a new economic form - digital economy, digital driving force to become the core of the digital economy. The continuous improvement of digital technology gives full play to the value of digitalization. In recent years, various digital technologies such as the Internet of Things, cloud computing and artificial intelligence have been constantly updated and gradually industrialized from experiment to practice, forming a complete digital value chain that has been applied in various fields, promoting the digitalization of various industries and creating new values for all industries. The rapid development of digital infrastructure drives the adoption of digitization. In recent years, China has been accelerating the construction of digital infrastructure, promoting the integrated innovation and application of industrial Internet, artificial intelligence, Internet of Things, Internet of vehicles, big data, cloud computing, block chain and other technologies, so as to make digital application more widely and deeply into all levels of social and economic operation and promote the development of digital economy.



As a traditional industry, the lawyer industry is still in the traditional handicraft era. Information is collected and sorted out by paper materials and stored in warehouses, which greatly affects efficiency. At present, in the midst of the epidemic, offline work is greatly restricted, and business will not be reduced because of the existence of restrictions. A large amount of business accumulation has brought great inconvenience, and the digital reform of the lawyer industry is imminent.



In the field of bankruptcy, the significance of meeting and voting is very important, which determines the trend of a bankruptcy project. In order to realize the digital transformation of bankruptcy business, it is essential to design a meeting system for bankruptcy project voting. Creditors of enterprise bankruptcy project are easy to reach the level of thousands or even ten thousand. If multiple meetings are held at the same time and voting is conducted in the same period, the concurrency will be greatly increased, causing great pressure on the server. Therefore, it is necessary to design and develop a meeting voting system specifically for high concurrency.



The research significance of comprehensive digitalization of creditor's rights meeting in the field of bankruptcy mainly includes the following three points:

One is that due to the COVID-19 pandemic, holding creditors' meetings online has become the main choice of managers. The advantages of online operation of bankruptcy cases represented by the network creditors' meeting are very obvious -- this advantage is not only reflected in the epidemic period, online operation is more convenient, fast, standardized and efficient in both program design and equipment use, and represents the future work trend of bankruptcy business. Network creditor's meeting is an innovation of the way of holding creditor's meeting by using network technology in the network era, which is conducive to improving work efficiency and better protecting creditor's rights. However, the network creditors' meeting is different from the traditional creditors' meeting, and many new problems need to be solved. Creditor's rights conference system is different from the conventional conference system, which is closely linked with the bankruptcy law. The conventional conference system is not applicable, so it is necessary to design and develop a targeted creditor's rights conference system.



Second, digitalization takes data as the main factor of production, converts all valuable people, things and things in the enterprise, such as business, production, marketing and customers, into digital stored data, forming data, information and knowledge that can be stored, calculated and analyzed. Together with external data obtained by the enterprise, Through the real-time analysis, calculation and application of these data can guide enterprises' production, operation and other businesses. And each creditor's rights meeting can produce a large amount of data, which can produce great economic value, so it is necessary to ensure the reliability of the storage of these data.



Third, with the rapid rise of computer technology and network technology in recent years, the Internet is changing people's way of production and life. The development of the Internet has brought about a surge in demand and pressure on technology, so the system architecture is constantly evolving, upgrading and iterating. From single application, to vertical split, to distributed services, to SOA, and now the hot microservices architecture. Although most of the problems have been solved, there are still some problems even when the traffic volume is relatively large, especially high concurrency and high availability still need a lot of design and research. For creditor's rights conference system, a creditor meeting is usually one thousand to ten thousand the number of levels, some even reach one hundred thousand level, if for many meetings at the same time, and meeting voting is usually concentrated in a period of time, that leads to the high concurrency issues, and the creditor meeting data very important, if the loss of important data or service suddenly lockout, Therefore, in the process of digitalization of creditor's rights meeting, the importance of targeted design with high concurrency and high availability is self-evident.



The main work of this thesis is the design and implementation of high concurrent video voting conference system. This topic will study how to design a system to meet the needs of legal cases of bankruptcy reorganization creditor's rights meeting and how to achieve it. The main research contents include the architecture design of the debt conference system in high concurrency scenario, the data storage design of the debt conference system in high concurrency scenario, the high availability of database in high concurrency scenario, and the front-end design and optimization of the debt conference system. The main work content is the creditor's rights conference system design and the creditor's rights conference system front and back end development and performance test.
\end{digest}
